---
#############################################################
#                                                           #
#   Click on "Knit" in RStudio to render this worksheet.    #
#                                                           #
#############################################################
title: "Import"
author: ""
date: ""
output: html_document
#############################################################
#                                                           #
#   Change the eval=FALSE to eval=TRUE to run the code      #
#                                                           #
#############################################################
params:
  sas_data_url: !r file.path("http://www.principlesofeconometrics.com/sas/medical.sas7bdat")
  sas_data_dir: !r c("../data/sas/")
---

```{r setup, include=FALSE}
library(rmarkdown)
library(knitr)
library(haven)
library(readxl)
library(openxlsx)
library(readr)
library(data.table)
options(repos = "https://cloud.r-project.org")
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE,
                      error = TRUE)
```

## Import Local SAS files

```{r import-local, eval=FALSE}
medical <- read_sas("../data/medical.sas7bdat", NULL)
View(medical)
```

## Download file, then import

Sometimes we want to use a URL to save the file, then import from a local folder. 
```{r download-sas, eval=FALSE}
download.file(
    url = "http://www.principlesofeconometrics.com/sas/medical.sas7bdat", destfile = "../data/downloads/medical.sas7bdat")
```

Now we can import from `../data/downloads/`

```{r import-download, eval=FALSE}
medical <- read_sas("../data/downloads/medical.sas7bdat")
```

## Importing with parameters

Add the following code to the YAML header (at the top of this file):

```{.yaml}
params:
  sas_data_url: !r file.path("http://www.principlesofeconometrics.com/sas/medical.sas7bdat")
  sas_data_dir: !r c("../data/sas/")
```

Now we can access the URL and downloads folder throughout the document using `params$sas_data_url` and `params$sas_data_dir`

```{r params, eval=FALSE}
params$sas_data_url
params$sas_data_dir
```

## Importing multiple data files 

What if we have a folder of SAS files we'd like to import? We can accomplish this with some help from `purrr` and R's `list.files()` function. 

```{r all_sas_data, eval=FALSE}
# create vector of files
sas_filenames <- list.files(params$sas_data_dir, full.names = TRUE)
# pass this vector 
all_sas_data <- sas_filenames |> 
    purrr::set_names() |> 
    map(.x = , .f = read_sas)
str(all_sas_data, list.len = 4)
```

