---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(pdgdev)
remove_prod_dir("test")
```

# pdgdev

<!-- badges: start -->
<!-- badges: end -->

The goal of `pdgdev` is to provide a set of tools for developing materials for PDG slides and materials. 

## Installation

This is a private repo, so only users can access. 


## Build development materials

Build production folder `foo`

```{r example}
library(pdgdev)
build_dev("foo")
```

Remove `foo` folder from development:

```{r}
remove_dev_dir("foo")
```

```{r}
fs::dir_tree("inst/dev/", recurse = FALSE)
```

## Copy development materials to production

After creating materials in `inst/dev/`, copy them into `inst/prod/` with `build_prod()`

```{r}
build_prod("test")
```

Remove `test` folder from production:

```{r}
remove_prod_dir("test")
```

```{r}
fs::dir_tree("inst/prod/", recurse = FALSE)
```


