---
title: "R Markdown Visualizations"
author: ""
date: ""
output: html_document
---

<!--
#############################################################
#                                                           #
#   Click on "Knit" in RStudio to render this worksheet.    #
#                                                           #
#############################################################
-->

```{r setup, include=FALSE}
library(knitr)
options(repos = "https://cloud.r-project.org")
knitr::opts_chunk$set(warning = FALSE, 
                    message = FALSE,
                    error = TRUE,
                    echo = TRUE,
                    dev = "ragg_png",
                    dpi = 320,
                    out.width = "80%",
                    fig.width = 6,
                    fig.asp = 0.618,
                    fig.retina = 2,
                    fig.align = "center",
                    fig.show = "hold")
```


# Load SmallNhanes

The `NHANES` package comes with data from the [2014 American National Health and Nutrition Examination surveys](http://www.cdc.gov/nchs/data/series/sr_02/sr02_162.pdf).

```{r}
SmallNhanes <- read_csv("https://bit.ly/nhanes-small") |> 
                janitor::clean_names() |> 
                mutate(health_gen = factor(x = health_gen, 
                               levels = c("Poor", "Fair", 
                                          "Good", "Vgood", 
                                          "Excellent"), 
                                ordered = TRUE))

head(SmallNhanes)
```

## First graph 

```{r}
SmallNhanes |> 
  ggplot(mapping = aes(x = weight, y = height)) + 
  geom_point() 
```

## Your Turn 1 

Set local vs. global aesthetic mappings

```{r}
# local 
# mapping = aes(x = weight, y = height)
SmallNhanes |> 
  ggplot() + 
  geom_point() + 
  geom_smooth()
```

```{r}
# global 
# mapping = aes(x = weight, y = height)
SmallNhanes |> 
  ggplot() + 
  geom_point() + 
  geom_smooth()
```

## Your Turn 2

How does BMI vary across levels of self-reported general health?

```{r , eval=FALSE}
SmallNhanes |>  
  ggplot() |> 
  geom_boxplot(mapping = aes(x = __________, y = ___))

```

## Your Turn 3

Fill in the code below to change the colors in the boxplot for each level of `health_gen`

```{r eval=FALSE}
SmallNhanes |> 
  ggplot() +
  geom_boxplot(
    aes(x = health_gen, y = bmi, _____ = health_gen))

```

## Layers

Combine the layers 

```{r}
SmallNhanes |>  
  ggplot(aes(x = weight, y = height)) + 
  geom_point(aes(color = gender))
```


```{r}
filter(SmallNhanes, gender == "male") |> 
  ggplot() + 
  geom_smooth(aes(x = weight, y = height), 
              color = "blue")
```


```{r}
filter(SmallNhanes, gender == "female") |> 
  ggplot() + 
  geom_smooth(aes(x = weight, y = height), 
              color = "red")
```

## Facets

```{r}
SmallNhanes |> 
  ggplot(aes(x = weight, y = height)) + 
  geom_point(aes(color = gender)) + 
  facet_wrap(race1 ~ gender)
```

