---
title: "R Markdown Tables"
author: ""
date: ""
output: 
  html_document:
    toc: true
    toc_float: yes
    code_folding: show
    self_contained: true
    
---

<!--
#############################################################
#                                                           #
#   Change the eval=FALSE to eval=TRUE to run the code      #
#                                                           #
#############################################################
-->

```{r setup, include=FALSE}
library(NHANES)
library(gtsummary)
library(rmarkdown)
options(repos = "https://cloud.r-project.org")
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE,
                      error = TRUE)
```

<!--
#############################################################
#                                                           #
#   Click on "Knit" in RStudio to render this worksheet.    #
#                                                           #
#############################################################
-->

## Import NHANES .csv file {.tabset}

Below we import a subset of the NHANES data from the [NHANES package](https://cran.r-project.org/web/packages/NHANES/index.html)

### Import 

Below we import the data with [`data.table::fread()`](https://datatable.readthedocs.io/en/latest/api/dt/fread.html)

```{r import-local, eval=TRUE}
nhanes_11_12 <- data.table::fread(input = "../data/csv/nhanes_11_12.csv")
glimpse(nhanes_11_12)
```

### Codebook

The variable names and definitions are below:

`id`: Participant identifier.

`gender`: Gender (sex) of study participant coded as `male` or `female`

`age`: Age in years at screening of study participant. Note: Subjects 80 years or older were recorded as 80.

`race3`: Reported race of study participant, including non-Hispanic Asian category: Mexican, Hispanic, White, Black, Asian, or Other. Not availale for 2009-10.

`education`: Educational level of study participant Reported for participants aged 20 years or older. One of 8thGrade, 9-11thGrade, HighSchool, SomeCollege, or CollegeGrad.

`hh_income`: Total annual gross income for the household in US dollars.

`poverty`: A ratio of family income to poverty guidelines. Smaller numbers indicate more poverty.

`weight`: Weight in kg

`height`: Standing height in cm. Reported for participants aged 2 years or older.

`bmi`: Body mass index (weight/height^2 in kg/m^2). Reported for participants aged 2 years or older.

`bp_sys_ave`: Combined systolic blood pressure reading, following the procedure outlined for BPXSAR.

`bp_dia_ave`: Combined diastolic blood pressure reading, following the procedure outlined for BPXDAR.

`testosterone`: Testerone total (ng/dL). Reported for participants aged 6 years or older. Not available for 2009-2010.

`tot_chol`: Total HDL cholesterol in mmol/L. Reported for participants aged 6 years or older.

`diabetes`: Study participant told by a doctor or health professional that they have diabetes. Reported for participants aged 1 year or older as Yes or No.

`sleep_hrs_night`: Self-reported number of hours study participant usually gets at night on weekdays or workdays. Reported for participants aged 16 years and older.

`phys_active_days`: Number of days in a typical week that participant does moderate or vigorous-intensity activity. Reported for participants 12 years or older.

## Calculate descriptives {.tabset}

We can calculate the descriptive statistics with [`dplyr`](https://dplyr.tidyverse.org/). 

### `descriptives`

```{r descriptives}
descriptives <- nhanes_11_12 |> 
    mutate(ht_meters = height*0.01, # calculate new vars
           bmi = weight/ht_meters^2) |> 
    group_by(diabetes) |> # calculate by diabetes
    summarise(n = n(), # get total
              across(c(age, bmi, bp_sys_ave, tot_chol), # numeric variables
              mean, na.rm = TRUE)) # calculate mean 
descriptives
```

### `big_descriptives`

```{r big_descriptives}
big_descriptives <- nhanes_11_12 |>
    dplyr::select(-id) |> # remove id
    dplyr::mutate(ht_meters = height * 0.01, # calculate new vars
                  bmi = weight / ht_meters ^ 2) |>
    dplyr::group_by(diabetes) |> # calculate by diabetes
    dplyr::summarise(n = n(), # get total
        dplyr::across(.cols = where(is.numeric), # all numeric variables
                      .fns =  mean, na.rm = TRUE)) # calculate mean 
big_descriptives
```

## `knitr::kable()` {.tabset}

Below are tables created with `knitr::kable()`

### Basic `kable` table 

```{r}
knitr::kable(descriptives)
```

### `kable` (`digits` & `col.names`)

```{r}
knitr::kable(descriptives, digits = 2, 
    col.names = c("Diabetic", "N", "Age", "BMI", 
        "Sys BP (Avg)", "Total Chol"))
```

### `kable` (`caption`)

```{r}
knitr::kable(descriptives, digits = 2, 
    col.names = c("Diabetic", "N", "Age", "BMI", 
        "Sys BP (Avg)", "Total Chol"), 
    caption = "Descriptive Statistics")
```



## `rmarkdown::paged_table()`

`paged_table()`s are great for larger tables (but don't work very well with PDFs)

```{r}
rmarkdown::paged_table(big_descriptives)
```


## `gtsummary::tbl_cross()` {.tabset}

The `gtsummary` package builds beautiful html tables. We'll cover `tbl_cross()` and `tbl_summary()` below.

`tbl_cross()` gives counts/percents of two categorical variables.

### Basic `tbl_cross()`

Below is a basic example of a cross-tabs table with `gtsummary`. 

```{r}
library(gtsummary)
tbl_vars <- dplyr::select(nhanes_11_12, 
        diabetes, race3)
gtsummary::tbl_cross(
    data = tbl_vars,
    row = race3, col = diabetes)
```


### `tbl_cross()` labels

Add lables with the [`labelled` package.](https://cran.r-project.org/web/packages/labelled/vignettes/intro_labelled.html) 

```{r}
library(labelled)
var_label(tbl_vars) <- list(
    race3 = "Race",
    diabetes = "Diabetes Status")
tbl_cross(data = tbl_vars, 
    row = race3, col = diabetes)
```

### `%`s and p-values

`gtsummary` had multiple options for adding percentages, p-values, and more.

```{r}
var_label(tbl_vars) <- list(
    race3 = "Race",
    diabetes = "Diabetes Status")
tbl_cross(data = tbl_vars, 
    row = race3, col = diabetes, 
    percent = "cell") |> 
    add_p() 
```

## `gtsummary::tbl_summary()` {.tabset}

The `gt_summary::tbl_summary()` function creates publication-quality summary tables with multiple statistical summary options.

### Basic `tbl_summary()`

```{r}
tbl_vars <- nhanes_11_12 |> 
    dplyr::mutate(ht_meters = height*0.01,
           bmi = weight/ht_meters^2) |> 
    dplyr::select(age, gender, 
        bmi, bp_sys_ave, bp_dia_ave)
var_label(tbl_vars) <- list(
    age = "Age",
    gender = "Gender",
    bmi = "BMI",
    bp_sys_ave = "Sys Avg",
    bp_dia_ave = "Dia Avg")
gtsummary::tbl_summary(tbl_vars)
```

### Grouped `tbl_summary()`

```{r}
tbl_vars <- nhanes_11_12 |> 
    dplyr::mutate(
     ht_meters = height*0.01,
     bmi = weight/ht_meters^2,
     diabetes = if_else(diabetes == "Yes", 
                 "Diabetic", "Healthy")) |> 
    dplyr::select(age, diabetes, gender, 
        bmi, bp_sys_ave, bp_dia_ave)
var_label(tbl_vars) <- list(
    age = "Age",
    diabetes = "Diabetic",
    gender = "Gender",
    bmi = "BMI",
    bp_sys_ave = "Sys Avg",
    bp_dia_ave = "Dia Avg")
gtsummary::tbl_summary(tbl_vars, 
    by = diabetes)
```

## Summary 

The average age in `nhanes_11_12` is `r round(mean(nhanes_11_12$age, na.rm = TRUE), 2)`. The correlation between age and average systolic blood pressure is `r round(cor(x = nhanes_11_12$age, y = nhanes_11_12$bp_sys_ave), 2)`

