---
title: "R Markdown Basics"
author: ""
date: ""
output: html_document
---

<!--
#############################################################
#                                                           #
#   Click on "Knit" in RStudio to render this worksheet.    #
#                                                           #
#############################################################
-->

```{r setup, include=FALSE}
library(knitr)
options(repos = "https://cloud.r-project.org")
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE,
                      error = TRUE)
```

## R Markdown

This is an [R Markdown document](http://rmarkdown.rstudio.com). When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

