---
#############################################################
#                                                           #
#   Click on "Knit" in RStudio to render this worksheet.    #
#                                                           #
#############################################################
title: "Objects in R"
author: ""
date: ""
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
options(repos = "https://cloud.r-project.org")
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE,
                      error = TRUE)
```

## Atomic vectors

### Creating vectors

Create logical, integer, double, and character vectors below

```{r , eval=FALSE}
______ <- c(TRUE, FALSE)
______ <- c(4L, 7L)
______ <- c(2.2, 8.09)
______ <- c("A", "D")
```

### Check `typeof()` 

```{r , eval=FALSE}
typeof(______)
typeof(______)
typeof(______)
typeof(______)
```

### Check `class()`

```{r , eval=FALSE}
class(______)
class(______)
class(______)
class(______)
```

## S3 Vectors 

```{r , eval=FALSE}
# create fct_vec
______ <- factor(
        x = c("Medium", "Low", "High"), 
        levels = c("Low", "Medium", "High"))
# create date_vec
______ <- c(Sys.Date(), Sys.Date() + 1)
# create dt_vec
______ <- c(Sys.time(), Sys.time() + (86400*365))
# create difft_vec
______ <- difftime(
            time1 = Sys.time(), 
            time2 = Sys.time() + (86400*365), 
            units = "days")
```

### Check `typeof()` 

```{r , eval=FALSE}
typeof(______)
typeof(______)
typeof(______)
typeof(______)
```

### Check `class()`

```{r , eval=FALSE}
class(______)
class(______)
class(______)
class(______)
```

### Check `attributes()`

Factor attributes

```{r , eval=FALSE}
attributes(______)
```

Date/Datetime attributes

```{r , eval=FALSE}
attributes(______)
attributes(______)
```

Difftime attributes

```{r , eval=FALSE}
attributes(______)
```

## Lists 

Create atomic list 

```{r , eval=FALSE}
atomic_list <- list(
    'logical vector' = ______,
    'integer vector' = ______,
    'double vector' = ______,
    'character vector' = ______
)
atomic_list
```


Create s3_list 

```{r , eval=FALSE}
s3_list <- list(
    'date vector' = ______,
    'datetime vector' = ______,
    'difftime vector' = ______
)
s3_list
```

Create list of lists

```{r , eval=FALSE}
vector_list <- list(
    'S3 list' = ______,
    'Atomic list' = ______
)
vector_list
```

## Data frames 

Create my_df from the logical, integer, double, 

```{r , eval=FALSE}
my_df <- data.frame(
    log_col = ______,
    int_col = ______,
    dbl_col = ______,
    chr_col = ______,
    date_col = ______,
    dt_col = ______
)
my_df
```

### Check structure 

```{r , eval=FALSE}
str(______)
```

### Check `class()`

```{r , eval=FALSE}
class(______)
```

### Check `typeof()` 

```{r , eval=FALSE}
class(______)
```

## Tibbles

```{r , eval=FALSE}
my_tbl <- tibble(
    log_col = ______,
    int_col = ______,
    dbl_col = ______,
    chr_col = ______,
    date_col = ______,
    dt_col = ______
)
my_tbl
```


### Check structure 

```{r , eval=FALSE}
str(______)
```

### Check `class()`

```{r , eval=FALSE}
class(______)
```

### Check `typeof()` 

```{r , eval=FALSE}
class(______)
```
